---
title: "About GT"
author: "giddybb"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
summary: Zig-Zag GT team information including cup history graphs.
tags:
- GT
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::read_chunk(paste0(rprojroot::find_rstudio_root_file(), "/content/project/common_project_code.R"))

```


```{r setup, include=FALSE}
```


```{r cleancalculate, echo=FALSE, message=FALSE, warning=FALSE}

```




```{r, echo=FALSE, message=FALSE, warning=FALSE}
these_matches <- all_matches %>% filter(teamname=="GT", !is.na(result)) %>% arrange(-event_no, -round_number)
results <- these_matches  %>% pull(result) 
recent_results <- head(results, 15)
n_wins <- sum(results =="wins")
n_losses <- sum(results=="losses")
n_matches <- length(results)
win_percentage <- 100*n_wins/n_matches

n_recent_wins <- sum(recent_results =="wins")
n_recent_losses <- sum(recent_results=="losses")
n_recent_matches <- length(recent_results)
recent_win_percentage <- 100*n_recent_wins/n_recent_matches

current_cups <- these_matches %>% slice(1) %>% pull(zz_cups_before)
current_rank <- these_matches %>% slice(1) %>% pull(zz_rank_before)
last_opponent <- these_matches %>% slice(1) %>% pull(opposition)
last_round <- these_matches %>% slice(1) %>% pull(event_round)


```

Zig-Zag GT is the third team in the Zig-Zag family. It was formed at the end of December 2019 (during the Let it Slide event) as an academy team for Zig-Zag. It was known as Zig-Zag Racerz. It changed its name to Zig-Zag GT after merging with parts of two other teams: first, the leadership of GrandTour (formerly Khaleesi) and second, parts of GreasySpanner.

GT currently has `r current_cups` cups and is ranked `r current_rank` in the world. This was measured going into the match against `r last_opponent` (`r last_round`).

Since formation GT has played `r n_matches` matches, winning `r n_wins` of those (a win percentage of `r round(win_percentage)`%). Of their most recent `r n_recent_matches` matches GT have won `r n_recent_wins` (a recent win percentage of `r round(recent_win_percentage)`%).  

Performance data for GT is stored on this [google sheet](https://docs.google.com/spreadsheets/d/1oGTfeDSjWoqHaOZYrw09kMxP42bo_sBBVVKJbEThsMI/edit?usp=sharing)

The two graphs below show the cup history of GT First, the cup progress over time with opposition names:

```{r, echo=FALSE, message=FALSE, warning=FALSE}


all_matches %>%
  filter(teamname=="GT", !is.na(zz_cups_before)) %>%
  ggplot(aes(x=match_number, y=zz_cups_before)) +
  geom_point() +
  geom_line() +
  geom_label_repel(size=1, aes(label=opposition))+
  theme_bw() +
  labs(y="cups")


```


Second, the cup progress relative to the other Zig-Zag teams. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

all_matches %>%
  ggplot(aes(x=round_number, y=zz_cups_before)) +
  geom_line(size=1, aes(colour=teamname)) +
  theme_bw() +
  labs(y="cups")
```



