---
title: "Merging GS and GT"
author: "gidddybb"
date: "14/05/2020"
output: html_document
summary: Information about player current locations and final destinations for GS and GT player merging.
tags:
- zz2
- zz3
---

On Monday 18 May 2020 the current players in Zig-Zag GS and Zig-Zag GT will be reorganised into two new teams. One of the teams will assemble in the current Zig-Zag GT team, this will be a competitive team looking to move up the ranks. The other will assemble in Zig-Zag GB. Zig-Zag GB will be a new team with zero cups to give players easy wins and big rewards.  

The page identifies which team each player has been assigned to.  
The destinations for current Zig-Zag GS Players can be found [here](#gs-destinations).  
The destinations for current Zig-Zag GT Players can be found [here](#gt-destinations)  

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::read_chunk(paste0(rprojroot::find_rstudio_root_file(), "/content/project/common_project_code.R"))

```


```{r setup, include=FALSE}
```


```{r cleancalculate, echo=FALSE, message=FALSE, warning=FALSE}
```

## GS Destinations

The table below gives the desintations for current Zig-Zag GS players. After you have collected your weekly chest on Monday morning, all players should leave Zig-Zag GS. If your destination is GT you should move to Zig-Zag GT. If your destination is GB you should move to Zig-Zag GB. If your name does not appear on the list, just ask in chat or on Discord.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
gs_results %>% 
  filter(Current=="y") %>%
  dplyr::select(Players, Destination)%>%
  arrange(Players) %>%
  mutate(Destination=ifelse(!is.na(Destination) & Destination==1, "GT", "GB"),
         Destination=cell_spec(Destination, color=ifelse(Destination=="GT", "purple", "blue"))) %>%
         #Destination=cell_spec(Destination, color=ifelse(Destination=="GT", "black", "blue"))) %>%
  kable(escape=F) %>%
  kable_styling(c("striped"), full_width = T, font_size = 11)
```

## GT Destinations
The table below gives the desintations for current Zig-Zag GT players. If your destination is GT you do not need to do anything - you should stay put. If your destination is GB, then after you have collected your weekly chest on Monday morning, you should leave Zig-Zag GT and join Zig-Zag GB instead. If your name does not appear on the list, just ask in chat or on Discord.
```{r, echo=FALSE, message=FALSE, warning=FALSE}
gt_results %>% 
  filter(Current=="y") %>%
  dplyr::select(Players, Destination)%>%
  arrange(Players) %>%
  mutate(Destination=ifelse(!is.na(Destination) & Destination==1, "GT", "GB"),
         Destination=cell_spec(Destination, color=ifelse(Destination=="GT", "purple", "blue"))) %>%
         #Destination=cell_spec(Destination, color=ifelse(Destination=="GT", "black", "blue"))) %>%
  kable(escape=F) %>%
  kable_styling(c("striped"), full_width = T, font_size = 11)
```


