---
title: "About GTS"
author: "giddybb"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
summary: Zig-Zag GTS team information including cup history graphs.
tags:
- GT
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::read_chunk(paste0(rprojroot::find_rstudio_root_file(), "/content/project/common_project_code.R"))

```


```{r setup, include=FALSE}
```


```{r cleancalculate, echo=FALSE, message=FALSE, warning=FALSE}

```




```{r, echo=FALSE, message=FALSE, warning=FALSE}
these_matches <- all_matches %>% filter(teamname=="GTS", !is.na(result)) %>% arrange(-event_no, -round_number)
inc_current_match <- all_matches %>% filter(teamname=="GTS", !is.na(opposition), !is.na(zz_cups_before), !is.na(zz_rank_before)) %>% arrange(-event_no, -round_number)
results <- these_matches  %>% pull(result) 
recent_results <- head(results, 15)
n_wins <- sum(results =="wins")
n_losses <- sum(results=="losses")
n_matches <- length(results)
win_percentage <- 100*n_wins/n_matches

n_recent_wins <- sum(recent_results =="wins")
n_recent_losses <- sum(recent_results=="losses")
n_recent_matches <- length(recent_results)
recent_win_percentage <- 100*n_recent_wins/n_recent_matches

current_cups <- inc_current_match %>% slice(1) %>% pull(zz_cups_before)
current_rank <- inc_current_match %>% slice(1) %>% pull(zz_rank_before)
last_opponent <- inc_current_match %>% slice(1) %>% pull(opposition)
last_round <- inc_current_match %>% slice(1) %>% pull(event_round)


```

Zig-Zag GTS is the second team in the Zig-Zag family. It was formed in May 2020 (during the Timesplitting event) as a combination of the top players in Zig-Zag GS (former ZZ second team) and Zig-Zag GT (former ZZ academy team). 

GTS  was last recorded as having `r format(current_cups, scientific=FALSE)` cups and being ranked `r current_rank` in the world. This measurement was taken going into the match against `r last_opponent` (`r last_round`).

Since formation GTS has played `r n_matches` matches, winning `r n_wins` of those (a win percentage of `r round(win_percentage)`%). Of their most recent `r n_recent_matches` matches GT have won `r n_recent_wins` (a recent win percentage of `r round(recent_win_percentage)`%).  

Performance data for GTS is stored on this [google sheet](https://docs.google.com/spreadsheets/d/1oGTfeDSjWoqHaOZYrw09kMxP42bo_sBBVVKJbEThsMI/edit?usp=sharing)

The two graphs below show the cup history of GTS First, the cup progress over time with opposition names:

```{r, echo=FALSE, message=FALSE, warning=FALSE}


all_matches %>%
  filter(teamname=="GTS", !is.na(zz_cups_before)) %>%
  ggplot(aes(x=match_number, y=zz_cups_before)) +
  geom_point() +
  geom_line() +
  geom_label_repel(size=2, aes(label=opposition))+
  theme_bw() +
  labs(y="cups")


```


Second, the cup progress relative to the other Zig-Zag teams. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

all_matches %>%
  ggplot(aes(x=round_number, y=zz_cups_before)) +
  geom_line(size=1, aes(colour=teamname)) +
  theme_bw() +
  labs(y="cups")
```


```{r}
the_table <- all_matches %>%
  arrange(-event_no, -special_round) %>%
  filter(teamname=="GTS") %>%
  mutate(opposition = paste0(opposition, " (cups:", opp_cups_before, "; rank: ", opp_rank_before, ")"))%>%
  dplyr::select(event_round, opposition, zz_points, opp_points, zz_cups_before, zz_cup_change, result) 

wins <- which(the_table$result=="wins")
losses <- which(the_table$result=="losses")
the_table%>%
  dplyr::select(-result) %>%
  kable(booktabs = T) %>%
  kable_styling() %>%
  row_spec(wins, bold = TRUE, color = "black", background = "lightgreen") %>%
  row_spec(losses, bold = TRUE, color = "black", background = "red") 
  
```

