---
title: "About RZR"
author: "giddybb"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
summary: Zig-Zag RZR team information including cup history graphs.
tags:
- RZR
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::read_chunk(paste0(rprojroot::find_rstudio_root_file(), "/content/project/common_project_code.R"))

```


```{r setup, include=FALSE}
```


```{r cleancalculate, echo=FALSE, message=FALSE, warning=FALSE}

```




```{r, echo=FALSE, message=FALSE, warning=FALSE}
these_matches <- all_matches %>% filter(teamname=="RZR", !is.na(result)) %>% arrange(-event_no, -round_number)
inc_current_match <- all_matches %>% filter(teamname=="RZR", !is.na(opposition), !is.na(zz_cups_before), !is.na(zz_rank_before)) %>% arrange(-event_no, -round_number)
results <- these_matches  %>% pull(result) 
recent_results <- head(results, 15)
n_wins <- sum(results =="wins")
n_losses <- sum(results=="losses")
n_matches <- length(results)
win_percentage <- 100*n_wins/n_matches

n_recent_wins <- sum(recent_results =="wins")
n_recent_losses <- sum(recent_results=="losses")
n_recent_matches <- length(recent_results)
recent_win_percentage <- 100*n_recent_wins/n_recent_matches


current_cups <- inc_current_match %>% slice(1) %>% pull(zz_cups_before)
current_rank <- inc_current_match %>% slice(1) %>% pull(zz_rank_before)
last_opponent <- inc_current_match %>% slice(1) %>% pull(opposition)
last_round <- inc_current_match %>% slice(1) %>% pull(event_round)


```

Zig-Zag RZR is the first team in the Zig-Zag family. RZR was formed (as Zig-Zag Racers)  at the end of June 2019 (at the start of the Newfangled vehicles event). It was born from the embers of rizzlaracers, a some time top 30 team brought down by an inactive leader.    

RZR  was last recorded as having `r format(current_cups, scientific=FALSE)` cups and being ranked `r current_rank` in the world. This measurement was taken going into the match against `r last_opponent` (`r last_round`).

Since formation RZR has played `r n_matches` matches, winning `r n_wins` of those (a win percentage of `r round(win_percentage)`%). Of their most recent `r n_recent_matches` matches RZR have won `r n_recent_wins` (a recent win percentage of `r round(recent_win_percentage)`%).  

Performance data for RZR stored on this [google sheet](https://docs.google.com/spreadsheets/d/1ftRMXTRL84SO-eedX8EIof8i_5C64qemwskffr8DUXA/edit?usp=sharing)

The two graphs below show the cup history of RZR. First, the cup progress over time with opposition names:

```{r, echo=FALSE, message=FALSE, warning=FALSE}


all_matches %>%
  filter(teamname=="RZR", !is.na(zz_cups_before)) %>%
  ggplot(aes(x=match_number, y=zz_cups_before)) +
  geom_point() +
  geom_line() +
  geom_label_repel(size=1, aes(label=opposition))+
  theme_bw() +
  labs(y="cups")


```


Second, the cup progress relative to the other Zig-Zag teams. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

all_matches %>%
  ggplot(aes(x=round_number, y=zz_cups_before)) +
  geom_line(size=1, aes(colour=teamname)) +
  theme_bw() +
  labs(y="cups")
```



