---
title: "About RZR"
author: "giddybb"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
summary: Zig-Zag RZR team information including cup history graphs.
tags:
- RZR
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::read_chunk(paste0(rprojroot::find_rstudio_root_file(), "/content/project/common_project_code.R"))

```


```{r setup, include=FALSE}
```


```{r cleancalculate, echo=FALSE, message=FALSE, warning=FALSE}

```




```{r, echo=FALSE, message=FALSE, warning=FALSE}
these_matches <- all_matches %>% filter(teamname=="RZR", !is.na(result)) %>% arrange(-event_no, -round_number)
inc_current_match <- all_matches %>% filter(teamname=="RZR", !is.na(opposition), !is.na(zz_cups_before), !is.na(zz_rank_before)) %>% arrange(-event_no, -round_number)
results <- these_matches  %>% pull(result) 
recent_results <- head(results, 15)
n_wins <- sum(results =="wins")
n_losses <- sum(results=="losses")
n_matches <- length(results)
win_percentage <- 100*n_wins/n_matches

n_recent_wins <- sum(recent_results =="wins")
n_recent_losses <- sum(recent_results=="losses")
n_recent_matches <- length(recent_results)
recent_win_percentage <- 100*n_recent_wins/n_recent_matches


current_cups <- inc_current_match %>% slice(1) %>% pull(zz_cups_before)
current_rank <- inc_current_match %>% slice(1) %>% pull(zz_rank_before)
last_opponent <- inc_current_match %>% slice(1) %>% pull(opposition)
last_round <- inc_current_match %>% slice(1) %>% pull(event_round)


```

Zig-Zag RZR is the first team in the Zig-Zag family. RZR was formed (as Zig-Zag Racers)  at the end of June 2019 (at the start of the Newfangled vehicles event). It was born from the embers of rizzlaracers. Rizzlaracers was a top team (briefly world number one and consistently top thirty) brought down by an inactive leader. 

The team merged with GreasySpanner and London UK after 110 matches. We experienced an extended period of stagnation in ranking, where we did not seem able to break into the top 100. After this, and specifically after yet another loss to Triglav in our 134th match, our then leader Layoo and now leader Kevin began heroic efforts of team tracking, with carefully considered delays in matchmaking. The impact of this on our rise in the rankings is clear below. 

RZR  was last recorded as having `r format(current_cups, scientific=FALSE)` cups and being ranked `r current_rank` in the world. This measurement was taken going into the match against `r last_opponent` (`r last_round`).

Since formation RZR has played `r n_matches` matches, winning `r n_wins` of those (a win percentage of `r round(win_percentage)`%). Of their most recent `r n_recent_matches` matches RZR have won `r n_recent_wins` (a recent win percentage of `r round(recent_win_percentage)`%).  

Performance data for RZR stored on this [google sheet](https://docs.google.com/spreadsheets/d/1ftRMXTRL84SO-eedX8EIof8i_5C64qemwskffr8DUXA/edit?usp=sharing)

The four graphs below show the cup and rank history of RZR. 

First, the cup progress over time (full details including opposition names are in the table below):

```{r, echo=FALSE, message=FALSE, warning=FALSE}


all_matches %>%
  filter(teamname=="RZR", !is.na(zz_cups_before)) %>%
  ggplot(aes(x=match_number, y=zz_cups_before)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept=110) +
  annotate(x=110, y=2000, geom="text", label="mergers", vjust=1, angle=90) +
  geom_vline(xintercept=135) +
  annotate(x=135, y=2000, geom="text", label="Layoo starts tracking", vjust=1, angle=90) +
  # geom_label_repel(size=1, aes(label=opposition))+
  theme_bw() +
  labs(y="cups")


```

Second, the progress of RZR in terms of world rank

```{r, echo=FALSE, warning=FALSE, message=FALSE}
all_matches %>%
  filter(teamname=="RZR", !is.na(zz_rank_before)) %>%
  ggplot(aes(x=match_number, y=zz_rank_before)) +
  geom_line() +
  # geom_label_repel(size=1, aes(label=opposition))+
  theme_bw() +
  labs(y="rank") +  
  scale_y_reverse(limits=c(NA, 1)) +
  geom_hline(yintercept=1) +
  annotate(x=100, y=1, geom="text", label="world rank 1", vjust=1)+
  geom_hline(yintercept=100) +
  annotate(x=170, y=100, geom="text", label="world rank 100", vjust=1)+
  geom_hline(yintercept=200) +
  annotate(x=170, y=200, geom="text", label="world rank 200", vjust=1) +
  geom_vline(xintercept=110) +
  annotate(x=110, y=250, geom="text", label="mergers", vjust=1, angle=90) +
  geom_vline(xintercept=135) +
  annotate(x=135, y=220, geom="text", label="Layoo starts tracking", vjust=1, angle=90) +
  geom_label_repel(data = all_matches %>%
                     filter(teamname=="RZR",
                            !is.na(zz_rank_before)) %>%
                     arrange(-match_number) %>%
                     slice(1)
                   ,
                   aes(label=zz_rank_before))
  


```

Third, the cup progress relative to the other Zig-Zag teams. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

all_matches %>%
  ggplot(aes(x=round_number, y=zz_cups_before)) +
  geom_line(size=1, aes(colour=teamname)) +
  theme_bw() +
  labs(y="cups")
```

Finally, the rank progress relative to the other Zig-Zag teams. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

all_matches %>%
  filter(!is.na(zz_rank_before)) %>%
  ggplot(aes(x=round_number, y=zz_rank_before, colour=teamname)) +
  geom_line(size=1.5) +
  theme_bw() +
  labs(y="rank") +  
  scale_y_reverse(limits=c(NA, 1)) +
  geom_hline(yintercept=1) +
  annotate(x=75, y=1, geom="text", label="world rank 1", vjust=1)+
  geom_hline(yintercept=100) +
  annotate(x=170, y=100, geom="text", label="world rank 100", vjust=1)+
  geom_hline(yintercept=200) +
  annotate(x=170, y=200, geom="text", label="world rank 200", vjust=1) +
  coord_cartesian(ylim=c(1000, 0))
```


```{r, echo=FALSE, warning=FALSE}
the_table <- all_matches %>%
  arrange(-event_no, -special_round) %>%
  filter(teamname=="RZR") %>%
  mutate(opposition = paste0(opposition, " (cups:", opp_cups_before, "; rank: ", opp_rank_before, ")"))%>%
  mutate(zz_cup_change=ifelse(is.na(zz_cup_change), zz_cups_after-zz_cups_before, zz_cup_change)) %>%
  dplyr::select(event_round, opposition, zz_points, opp_points, zz_cups_before, zz_cup_change, result)
  

wins <- which(the_table$result=="wins")
losses <- which(the_table$result=="losses")
the_table%>%
  dplyr::select(-result) %>%
  kable(booktabs = T) %>%
  kable_styling() %>%
  row_spec(wins, bold = TRUE, color = "black", background = "lightgreen") %>%
  row_spec(losses, bold = TRUE, color = "black", background = "red") 
  
```
